--- 
title: "A step-by-step workflow for low-level analysis of single-cell RNA-seq data with Bioconductor"
author: "Kwesi Kumi, Noah Cupp, Duong, Kashif Mashood
format: html
---

## Introduction
Single cell RNA sequencing measures gene expression in individual cells. It is able to provide significant insight on cellular diverstiy as it is used to detect changes in gene expression during the onset and progression of diseases or treatment response.

## Package Installation
Here is the code to install the simpleSingleCell package

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("scRNAseq")
```


## Data Overview
## Data Loading an Annotation
The data that was chosen for this analysis was a mouse haematopoetic stem cell (HSC) dataset generated with Smart-seq2. 

```{r}
library(scRNAseq)
library(AnnotationHub)

sce.nest <- NestorowaHSCData()

ens.mm.v97 <- AnnotationHub()[["AH73905"]]
anno <- select(ens.mm.v97, keys=rownames(sce.nest), 
    keytype="GENEID", columns=c("SYMBOL", "SEQNAME"))
rowData(sce.nest) <- anno[match(rownames(sce.nest), anno$GENEID),]
```


